---
title: "Demo"
output:
  html_document:
    number_sections: yes
date: "2024-08-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Markdown

```{r, include=FALSE}
auburn_university <- 3
```

<!-- This document is for class purposes. -->

This is an example text. More specifically an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see [Google](https://google.com). We may need to include some values in the output: we can use some inline code as follows where we mention Auburn University `r auburn_university`. Or we can add statistics on the data, where the average speed is `r mean(cars$speed)*auburn_university`.

When you click the *Knit* button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars, eval = F}
summary(cars) # this code gives an overview of the dataset
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

# Equations

You can include inline equations as follows $\alpha = 4$. But you can also create blocks of equations: 

$$\sum \alpha \pm \beta $$

# Loading Data

The following command loads data from my desktop:

```{r}
rob <- read.csv("adult.csv", row.names=1, sep=";")
```

Another option is to open a window for the user to select the data. The user should copy-paste this code into their console in R:

```{r, eval=F}
rob <- read.csv(file.choose(), row.names=1, sep=";")
```

If you want to use the above code, you can download the data from the following link: <https://www.kaggle.com/datasets/wenruliu/adult-income-dataset>.